Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-15 ms.tex
added ms

EDITING HERE: Double check that petrillo paper
operates in image space.

@@

% Augmenting dataset
To augment our training set, we rotated each image in the set by
multiples of $90^o$.  Augmenting our data by a factor of four
naturally optimizes the use of available training data, since our
feature extraction method of HOG is not rotationally invariant.  This
has an equivalent improvement to the study illustrated in
Figure~\ref{fig:trainsizeLSST10}.

@@

% Benefits of our method
We emphasize that classical linear classifiers, such as logistic
regression, is scalable and relatively easy to parallelize with open
source tools such as {\em Spark}.  Initial checks indicated that HOG
features are well separated enough for a linear classifier algorithm.
Reproducible results do not require supercomputing resources.

>>>>

\todo{EDITING HERE: Double check that petrillo paper operates in image
  space, edit previous paragraph.}

@@

% Augmenting dataset
To augment our training set, we rotated each image in the set by
multiples of $90^o$.  Since our feature extraction method of HOG is
not rotationally invariant, augmenting our data by a factor of four
naturally optimizes the use of available training data.  This has an
equivalent improvement to the study illustrated in
Figure~\ref{fig:trainsizeLSST10}.

@@

% Benefits of our method
We emphasize that classical linear classifiers, such as logistic
regression, is scalable and relatively easy to parallelize with open
source tools such as \todo{\em Spark}\footnote{...spark...org}}.
  Initial checks indicated that HOG features are well separated enough
  for a linear classifier algorithm.  Reproducible results do not
  require supercomputing resources.
